Report on a Safety Checker for Petri nets

### 2014-02-01 paper/workspace/main.tex
Updated paper drafts

TODO

* Property: Thread 1 and Thread 2 are never in the critical section at the same time.

@@

  \end{verbatim}
\begin{align*}
  C =& \left( \bigwedge_{s \in S}
    s = M_0(s) + \sum_{t \in ^\bullet s} t - \sum_{t \in s^\bullet} t
  \right) \land \\
  & \left( \bigwedge_{s \in S} s \ge 0 \right) \land
    \left( \bigwedge_{t \in T} t \ge 0 \right)
\end{align*}

@@

\begin{verbatim}
  - Assignment A_\theta:
    id1        = true
    cs1        = false
    idle1      = false
    req1       = true
    nid1       = false
    id2        = true
    cs2        = false
    idle2      = false
    req2       = true
    after_you2 = true
    await2     = false
  - Refinement constraint \delta:
    id1 + id2 + req1 + req2 + after_you2 >= 1
    ^     ^     ^      ^      ^
    |     |     |      |      |
    ---------------------------
      |
      S = {iq1, iq2, req1, req2, after_you2}, therefore \delta excludes
      assignment A in the next iteration

@@

\end{verbatim}
\begin{align*}
  C_\theta =& \left( \bigwedge_{s \in S} \left( s \Rightarrow
        \bigwedge_{t \in s^\bullet} \bigvee_{p \in t^\bullet} p
    \right) \right) \land \\
  & \left( \bigvee_{s \in S: M_0(s) > 0} s \right) \land \\
  & \left( \bigwedge_{s \in S: A(s) > 0} \neg s \right) \\
\end{align*}
\begin{verbatim}

@@

\end{verbatim}
\begin{align*}
  & \delta = \left( \sum_{A_\theta(s)} s \ge 0 \right)\\
\end{align*}

>>>>

\includegraphics[scale=0.75]{lamport-code}

\begin{verbatim}
* Property: Thread 1 and Thread 2 are never in the critical section at the same time.

@@

  \end{verbatim}
\begin{align*}
  C(S, T, E, M_0) :=& \left( \bigwedge_{s \in S} \left(
    s = M_0(s) + \sum_{(t, s) \in E} t - \sum_{(s, t) \in E} t
  \right) \right) \land
    \left( \bigwedge_{s \in S} s \ge 0 \right) \land
    \left( \bigwedge_{t \in T} t \ge 0 \right)
\end{align*}

@@

\begin{verbatim}
  - Assignment A_\theta:
    id1        = true
    cs1        = false
    idle1      = false
    req1       = true
    nid1       = false
    id2        = true
    cs2        = false
    idle2      = false
    req2       = true
    after_you2 = true
    await2     = false

  - Refinement constraint \delta:
    id1 + id2 + req1 + req2 + after_you2 >= 1
    ^     ^     ^      ^      ^
    |     |     |      |      |
    ---------------------------
      |
      S = {iq1, iq2, req1, req2, after_you2}, therefore \delta excludes
      assignment A in the next iteration

@@

\end{verbatim}
\begin{align*}
  C_\theta(S, T, E, M_0) :=& \left( \bigwedge_{s \in S} \left( s \Rightarrow
      \bigwedge_{(s, t) \in E} \bigvee_{(t, p) \in E} p
    \right) \right) \land
    \left( \bigvee_{s \in S: M_0(s) > 0} s \right) \land
    \left( \bigwedge_{s \in S: A(s) > 0} \neg s \right)
\end{align*}
\begin{verbatim}

@@

\end{verbatim}
\begin{align*}
  & \delta(A_\theta) := \left( \sum_{A_\theta(s)} s \ge 0 \right)
\end{align*}
